To Do List

### 2019-08-23 Papers.Rmd
Add collinearity note
Add Peakachu paper

@@

>>>>

- Salameh, Tarik J, Xiaotao Wang, Fan Song, Bo Zhang, Sage M. Wright, Chachrit Khunsriraksakul, and Feng Yue. “A Supervised Learning Framework for Chromatin Loop Detection in Genome-Wide Contact Maps.” Preprint. Bioinformatics, August 20, 2019. https://doi.org/10.1101/739698. - Peakachu - loop prediction from Hi-C data using random forest. ChIA-PET and HiChIP provide positive training examples. H3K27ac HiChIP better predicts short-range interactions, CTCF ChIA-PET is better for longer interactions. Each pixel is characterized by 11x11 window, 10Kb resolution data, Gm12878 and K562 cell line. Excels for short-range interactions. Model trained using data from Hi-C performs well in other technologies, Micro-C, DNA SPRITE. Code athttps://github.com/tariks/peakachu, Predicted loops for 56 cell/tissue types are available athttp://promoter.bx.psu.edu/hi-c/publications.html

@@

- Check your (Mixed) Model for Multicollinearity with ‘performance’, https://www.r-bloggers.com/check-your-mixed-model-for-multicollinearity-with-performance/
